\documentclass[11pt,a4paper,sans]{moderncv}

% Moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Adjust the page margins
\usepackage[scale=0.75]{geometry}

% Personal data
\name{David Robert}{Koch}
% Contact details removed from public repo for privacy. Available upon request.
\address{}{}
\phone[mobile]{}
\email{}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\section{Summary}
Versatile Technical Specialist and Systems Architect with a background in Cloud Engineering, DevOps, and 3D Graphics. Expert in \textbf{Sovereign Systems Synthesis}—orchestrating agentic AI deployments (ELENA Framework), performing systematic security audits, and bridging generative AI workflows with local-first hardware architectures (AMD ROCm). Proven track record in managing cross-functional international teams and executing high-precision technical deployments.

\section{Analytical Profile}
\cvitem{Sovereign Agent Orchestration}{Architect of the \textbf{ELENA Framework}: a modular AI system (Manager, Worker, Evaluator, Lizard Brain) designed for local node sovereignty. Specialist in "Cogito Bridge" implementations for deterministic biometric state justification.}
\cvitem{Local-First AI Systems}{Expert in high-performance local AI clusters using \textbf{AMD ROCm} (RX 7900 XTX). Specialist in hardware-level optimizations (\texttt{HSA\_P2P\_DISABLE=1}) and kernel-level hardening for secure, private inference.}
\cvitem{Surgical AI \& Weight Surgery}{Specialist in "H-Neurons" analysis and weight surgery for llama-based architectures. Experienced in eliminating hallucinations by surgically zeroing specific linear layer biases (\texttt{b\_proj}).}

\section{Technical Projects}
\cvitem{ELENA Sovereign Agent Framework}{Developed a 4-module agentic architecture focusing on \textbf{Manager} (Strategic), \textbf{Worker} (Technical), \textbf{Evaluator} (QA), and \textbf{Lizard Brain} (Biometric State). Implemented "Cogito Bridge" for algorithmic honesty.}
\cvitem{The Infinity Fallacy}{Analytical research refuting multiverse-based historical determinism (Blown Out Back fallacy). Developed a mathematical framework for identifying and mitigating AI over-refusal through state justification.}
\cvitem{AMD ROCm Hardened Node}{Deployed a security-hardened local AI node on \textbf{AMD ROCm} hardware. Implemented 10-phase security audit protocols, kernel hardening (AppArmor/SELinux), and P2P communication optimizations.}

\section{Skills}
\cvitem{Programming}{Python, C, Linux/Windows Shell Scripting, C\#, C++, Rust (3D Graphics)}
\cvitem{Cloud/DevOps}{Linux (CachyOS/Arch), Kernel Hardening (AppArmor/SELinux), 10-Phase Security Auditing}
\cvitem{AI / Graphics}{ELENA Framework, AMD ROCm (P2P/GDN), Blender (5+ years), Unreal Engine, Quixel Megascans, MetaHuman, Qwen 3.5}
\cvitem{Languages}{German (Native), English (Full Professional Proficiency), French (Basic)}
\cvitem{Frameworks}{Agentic Tool-Use, RAG, Technical Translation, Team Leadership}

\section{Experience}
\cventry{AUG 2024--Present}{Co-Founder and Manager}{Dalmer Co., "Butter" Project}{Hamburg/Frankfurt (Remote)}{}{%
\begin{itemize}%%
\item Orchestrating German \& English cross-team efforts and technical communication.
\item Managing application translation pipelines (EN $\leftrightarrow$ DE).
\end{itemize}}

\cventry{JUNE 2024--JULY 2024}{Junior Cloud Engineer}{Imos GmbH}{G"oppingen (Hybrid Remote)}{}{%
\begin{itemize}%%
\item Virtual machine orchestration (e.g., macOS on Proxmox) and critical server maintenance.
\end{itemize}}

\cventry{JUNE 2021--Present}{Freelance Contractor / AI Specialist}{Independent}{Remote}{}{%
\begin{itemize}%%
\item Specialized in RLHF, agentic prompt engineering, and technical consulting for firms (dataannotation.tech, outlier.ai, micro1.ai).
\end{itemize}}

\cventry{AUGUST 2023--MAY 2024}{Junior DevOps Programmer}{Deutsche Telekom}{Bremen}{}{%
\begin{itemize}%%
\item Managed updates and security for Linux servers in telecommunication clusters.
\end{itemize}}

\cventry{2019}{Technical Assistant}{Elbe-Weser IT (Internship)}{Zeven / Elsdorf}{}{%
\begin{itemize}%%
\item Supported hardware maintenance and systems setup for professional IT environments.
\end{itemize}}

\section{Education}
\cventry{AUGUST 2022--JUNE 2023}{Game Design (Incomplete)}{Designschule}{Schwerin}{}{Focus on Game Art and Design.}
\cventry{AUGUST 2020--JUNE 2021}{Screen Design (Incomplete)}{Berufliche Schule}{Hamburg}{}{Specialization in Web Design and composition history.}
\cventry{AUGUST 2018--JUNE 2020}{Secondary Degree}{St. Viti Gymnasium}{Zeven}{}{Python and Game Design fundamentals.}
\cventry{AUGUST 2013--JUNE 2018}{High School Foundation}{St. Viti Gymnasium}{Zeven}{}{Member of \textbf{VitiBots} Robotics group and School Orchestra (Trombone).}

\section{Awards}
\cvitem{Robotics}{Recipient of multiple awards with group \textbf{VitiBots} for technical innovation.}

\end{document}